\clearpage
\appendix
\section{Artifact Description: \myTitle}

\kbf{This is close, some details need to be verified}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Abstract}

This artifact contains instructions on accessing the the following
data/utilities from the paper:
\begin{itemize}
        \item A script to properly configure the APEI error injection interface
                used in this work (if supported by platform)
        \item The error injection utility that injects errors at the period
                specified.
        \item The \selfish utility used to measure the overheads of the injected
                correctable errors.
        \item The \LogGOPSim simulator and application execution traces used for
                the correctable DRAM error logging impacts  experiments 
        \item The appropriate analysis and plotting scripts used in the paper
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Description}

\subsubsection{Check-list (artifact meta information)}

{\small
\begin{itemize}
        \item {\bf Program}: C++ for \LogGOPSim, C and {\texttt{cmake}} for
                \selfish, Python (numpy and matplotlib) for error injection, and
                {\texttt{bash}} for APEI configuration script.
        \item {\bf Compilation}: g++ and gcc 4.2+ for \LogGOPSim and \selfish,
                Python 2.7+ for the injection and analysis scripts.
        \item {\bf Data set}: In this paper, we analyzed a collection of application
                execution traces in our correctable DRAM error experiments.  The
                applications used were: LAMMPS-lj, LAMMPS-crack, LAMMPS-SNAP,
                LULESH, miniFE, SPARC, and CTH.  In addition, we also used execution
                traces for three microbenchmarks: allreduce, reduce, and stencil
                \kbf{Ensure these are correct}.
        \item {\bf Run-time environment}: Any modern Linux distribution
        \item {\bf Hardware}: Any for \LogGOPSim.  For DRAM Error INJection
                (EINJ) testing, a platform that support ACPI 5.0+ is needed.
        \item {\bf Experiment customization}: modify Makefile to specify different
                application traces.
        \item {\bf Publicly available?}: All but two of the execution traces
                (CTH and SPARC) is publicly  available.  Because CTH and SPARC
                are export-controlled, their traces cannot be released publicly.  
\end{itemize}
}

\subsubsection{How software can be obtained (if available)}
\begin{itemize}
\item \LogGOPSim is available at:\\
    \url{https://htor.inf.ethz.ch/research/LogGOPSim/LogGOPSim-1.1.tgz}.  

\item Error injection and \selfish scripts can be found in our repository at: 
    \detail{made up repo}
\end{itemize}

\subsubsection{Hardware dependencies}

\LogGOPSim will run on any modern general-purpose computer. However, the
largest application scale and duration that can be simulated depends on
available RAM.  Memory usage increases linearly in both and scale and application
runtime.

The hardware error injection scripts can only be run on a platform which fully
support the APEI interface defined in ACPI 5.0+ specification.  The majority of
modern production hardware the authors has access to \emph{do not} fully support
this specification.  Included in the repo (and detailed below) is a script to
test and configure a platform for this testing, if supported.

\subsubsection{Software dependencies}

Application simulations were run on a supercomputer running Linux located at
\detail{Sandia National Laboratories}. \LogGOPSim and the analysis scripts have
been tested on Linux and MacOS running Python 2.7, Matplotlib 2.0.0, and g++/gcc
4.2.1  The error injection scripts must be run on a modern Linux with a kernel
version of 3.10 or greater.

\subsubsection{Datasets}

\begin{table}
\centering
\begin{tabular}{ l c }
\toprule
LogGOPS parameter & Value\\
\midrule
\textcolor{red}{L}atency                & 1.8$\mu s$ \\
\textcolor{red}{o}verhead per message   & 12.4$\mu s$ \\
\textcolor{red}{g}ap per message        & 2.6$\mu s$  \\
\textcolor{red}{G}ap per byte           & 1$ns$     \\
\textcolor{red}{O}verhead per byte      & 0$ns$     \\
\textcolor{red}{S}: rendezvous threshold  & 65,536 bytes \\
\bottomrule
\end{tabular}
\caption{
  LogGOPS parameters used in our study. Values measured using~\cite{netgauge-web}
}
\label{tab:logp}
\end{table}

Application traces used (excluding CTH and SPARC) are located in the {\texttt{traces}} 
directory of our repository.  LogP parameters used are specified in \reftab{tab:logp}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Installation}

Installation instructions for \LogGOPSim is available at: \url{https://htor.inf.ethz.ch/research/LogGOPSim/}

Error injection and analysis utilities installation instruction:


\begin{Verbatim}[commandchars=\\\{\},frame=single]
 $ git clone \detail{A very fake repo}
\end{Verbatim}

\subsubsection{APEI Error INJection Installation (EINJ)}

The {\texttt{configure\_apei.sh}} script checks and properly installs system
software for error injection.  If script fails on any test, injection support is
not supported on architecture.  Script should be run on a Linux system, and with
{\texttt{root}} privileges.

\begin{Verbatim}[commandchars=\\\{\},frame=single]
 $ sudo configure_apei.sh
Checking kernel version: 3.10.0-229 \color{green}{PASS}
Checking kernel commandline:        \color{green}{PASS}
Checking for ACPI EINJ table: found \color{green}{PASS}
Checking for kernel modules:
 ... loading einj module            \color{green}{PASS}
Checking supported APEI error injection
types:
 0x00000008 Memory Correctable
 0x00000010 Memory Uncorrectable
non-fatal
 0x00000020 Memory Uncorrectable fatal
 0x00000040 PCI Express Correctable
 0x00000080 PCI Express Uncorrectable
non-fatal
 0x00000100 PCI Express Uncorrectable
fatal
                                    \color{green}{PASS}
Test Complete: \color{green}{PASS}
\end{Verbatim}


\subsubsection{Error Injection Utility}

If the {\texttt{configure\_apei.sh}} script from the previous sections completes
without error, error injection is possible on the platform.  The
{\texttt{error\_inject.py}} script included in the repo can be used to to inject
correctable (and detected, non -fatal uncorrectables as well).  Passing {\texttt{--help}}
to the script provides a descrition of the options (must be run as
{\texttt{root}} as well)

\begin{Verbatim}[commandchars=\\\{\},frame=single]
 $ ./error_inject.py --help
usage: error_inject.py [-h] [-i INTERVAL]
[-l LENGTH] [-c | -u] [-d] [-v]
[-a ADDR [ADDR ...]]

APEI error injection utility

optional arguments:
  -h, --help show this help
message and exit
  -i INTERVAL, --interval INTERVAL
Periodic interval in seconds to inject
memory errors
  -l LENGTH, --length LENGTH Length
in seconds to run application (default
1200 secs)
  -c, --dram-correctable Inject
DRAM correctable error (default on)
  -u, --dram-uncorrectable Inject
DRAM uncorrectable error non-fatal
(default off)
  -d, --dry-run         Dry-run,
do not actually inject the error
(default off)
  -v, --version         show
program's version number and exit
  -a ADDR [ADDR ...],
  --addr ADDR [ADDR ...] List
of address to inject into
(default 0x12345000)
 
\end{Verbatim}

As an example, if we want to inject correctable memory errors at an interval of
every 100 seconds, at addresses {\texttt{0x12345000}}, {\texttt{0x12346000}} and
{\texttt{0x123457000}} for 1400 seconds.

\begin{Verbatim}[commandchars=\\\{\},frame=single]
 $ sudo ./error_inject.py -i 100 -l 1400
-c -a 0x12345000 0x12346000 0x123457000
\end{Verbatim}

\subsubsection{Correctable Impacts Measurement}

The \selfish utility included in the repo can be used to measure the impact of
correctable errors.  \selfish is a C program that depends on the
{\texttt{gengetopt}}
utility~\footnote{\url{https://www.gnu.org/software/gengetopt/gengetopt.html}},
a C99 compliant compiler, {\texttt{cmake}}, and an MPI library. \selfish is
located in the {\texttt{tools/selfish}} directory of the repo.  Building and
running is done as follows:


\begin{Verbatim}[commandchars=\\\{\},frame=single]
 $ cd tools/selfish
 $ mkdir build
 $ cd build
 $ cmake ..
 -- Found gengetopt: /opt/local/bin/
gengetopt (2.22.6)
 -- Performing Test HAVE_NB_ALLREDUCE -
Success
 -- Have MPI_Iallreduce(), we are good
 -- Configuring done
 -- Generating done
 -- Build files have been written to:
${PWD}/build
 $ make 
Scanning dependencies of target selfish
 [ 83%] Building C object src/CMakeFiles/
selfish.dir/cmdline.c.o
 [ 91%] Building C object src/CMakeFiles/
selfish.dir/selfish.c.o
 [100%] Linking C executable selfish
 [100%] Built target selfish

\end{Verbatim}

Passing the {\texttt{--help}} option to \selfish gives command line options

\begin{Verbatim}[commandchars=\\\{\},frame=single]
 $ selfish --help
 usage: selfish [-h] [-t THRESHOLD]
[-l LENGTH]

OS jitter recording microbenchmark

  -h, --help Print help and exit
  -t, --threshold=INT Threshold.
Values less then are not recorded
(default= 150 nanoseconds)
  -l, --length=INT Collection duration
in seconds (default= 1200 seconds)

\end{Verbatim}

As an example, if we want to collect \selfish traces in $24$ cores on a node for
1200 seconds, and using the default $150$ nanosecond threshold.

\begin{Verbatim}[commandchars=\\\{\},frame=single]
 $ mpirun -n 24 ./selfish -l 1200

 Calibrated tps: [ 2.1e+09, 2.1e+09,
2.1e+09 ]

 Avg Bench Wall Time: 1200.44 secs.
 Avg File Write Time: 0.36 secs.
 Avg Total Kernel Time: 1200.00 secs.

 Workload: Selfish.
 Problem description: rtsc() threshold
timing
 Threshold: 150 nsecs (cycles: 314)

 Datapoints: [ 926097, 966200, 996097 ]
\end{Verbatim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experiment workflow}

\begin{Verbatim}[commandchars=\\\{\},frame=single]
  $ make DRAM-overheads # For \LogGOPSim
runs and correctable DRAM plots
\end{Verbatim}

\begin{Verbatim}[commandchars=\\\{\},frame=single]
  $ make analysis # For analysis plots
\end{Verbatim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evaluation and expected result}

All generated figures (excluding those from export-controlled applications) will
be placed in the {\texttt{figs}} directory

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experiment customization}

New application traces can be added for analysis by adding the new trace
directory to the {\texttt{APPLICATION\_TRACES}} variable in the top-level Makefile

New DRAM correctable noise traces can be added by modifying the
{\texttt{NOISE\_TRACES}} variable in that same Makefile

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Notes}

Using \LogGOPSim to simulate the execution of an application running on 
a large number of nodes can be very time-consuming.  In extreme cases,
it may take a day or more to simulate a few minutes of execution of
very large applications.

\clearpage
\section{Artifact Evaluation: \myTitle}

\subsection{Formula's Used for \Cref{tab:CE_rate}}
